\documentclass[10pt,a4paper]{article}
\usepackage[left=0.6in,right=0.6in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=14pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}
\begin{document}

{\LARGE \textbf{A.M. Kavindu Pramodya Abeysundara}} \\[2pt]
Software Engineer \
Colombo, Sri Lanka \
\href{mailto:kavindupramod55@gmail.com}{kavindupramod55@gmail.com} \quad | \quad +94 76 669 7286 \
\href{https://kavindupramod.netlify.app/}{Portfolio} \quad | \quad \href{https://github.com/KavinduPramod}{GitHub} \quad | \quad \href{https://linkedin.com/in/kavindupramod/}{LinkedIn}

%------------------------
\section*{Professional Summary}
Software Engineer experienced in building, deploying, and maintaining production systems across fintech, web, and mobile platforms. Specialized in backend engineering and DevOps with ownership of CI/CD pipelines, container infrastructure, and production deployments. Contributed to 35+ applications in a 17-member team, including 20+ live containerized systems in production.

%------------------------
\section*{Technical Skills}
\textbf{Languages:} Python, JavaScript, Java (basic) \
\textbf{Frameworks:} React, Flask, FastAPI, Electron \
\textbf{DevOps:} Docker, CI/CD, Linux servers, Git, GitHub workflows, private registries \
\textbf{Cloud:} DigitalOcean \
\textbf{Databases:} MariaDB, Redis \
\textbf{Other:} Build distribution systems, automated update delivery, production deployment

%------------------------
\section*{Experience}
\textbf{Software Engineer (Associate Title)} \hfill Aug 2023 -- Present \
\textbf{DiproIT Pvt Ltd — Colombo, Sri Lanka}
\begin{itemize}
\item Led build engineering and release distribution for the company's primary microfinance platform ensuring seamless automated updates.
\item Designed and maintained CI/CD pipelines that package and deploy build artifacts to Linux servers.
\item Managed containerized infrastructure for multiple production systems using Docker and private registries.
\item Deployed backend services for mobile apps published on Google Play.
\item Supported backend engineering and DevOps operations across fintech platforms and company websites.
\item Contributed to 35--40 projects with 20+ live systems currently running.
\item Collaborated within a 17-engineer team delivering scalable financial software.
\end{itemize}

%------------------------
\section*{Projects}
\textbf{MoodMirror (Final Year Project)} \
AI-powered system with modern backend architecture. \
\href{https://github.com/KavinduPramod/moodmirror}{GitHub Repository}
\vspace{4pt}
\textbf{AI Banker Platform (Web + Electron)} \
Microfinance platform with automated deployment and distribution infrastructure. \
\href{https://demo.aibanker.cloud/login}{Live Demo}
\vspace{4pt}
\textbf{Mirage Designs Deployment} \
Implemented system features and handled full production deployment. \
\href{https://miragedesigns.lk/}{Website}

%------------------------
\section*{Mobile App Deployments}
Backend deployment + production publishing:
\begin{itemize}
\item AI Banker Member App
\item Rajida Event App
\item Rajida Support Service
\end{itemize}

%------------------------
\section*{Education}
\textbf{BSc (Hons) Computer Science — Final Year} \
University of Westminster

%------------------------
\section*{Certifications \& Hackathons}
Object Oriented Programming (LinkedIn) \quad | \quad Python Essential Training (LinkedIn) \
React.js Essential Training (LinkedIn) \quad | \quad CodeSpring 7.0 \quad | \quad Open Hack 2.0 \quad | \quad Haxmas 2023

%------------------------
\section*{Strengths}
Production troubleshooting mindset • Linux environment expertise • Rapid tech adaptation • Independent deployment pipeline ownership
\end{document}